iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-28 manuscript/main.tex
better layout of link
removed superfluous word
RNA-seq

\subsection*{Single-cell plate-based RNA-seq}
% TODO: better title, or do we drop this allen section altogether?
We demonstrate the application of iSEE to examine a subset of 379 cells from of mouse visual cortex \citep{tasic2016allen}.

@@

This particular example can be reproduced locally after installation of the iSEE package with the following code:

\subsection*{Single-cell droplet-based RNA-seq}
% TODO: better title, or do we drop the allen section altogether (above)?
We also demonstrate the use of iSEE to explore a larger data set of 4,000 PBMC single-cell RNA sequencing dataset from 10X Genomics \citep{zheng2017massively}.
% TODO: take out the juice from what the tour does, and maybe one figure/screenshot in each case?
% embed the allen demo data set
\url{http://shiny.imbei.uni-mainz.de:3838/iSEE_PBMC4k/}

>>>>

\subsection*{Single-cell plate-based RNA-seq}
% TODO: better title, or do we drop this allen section altogether?
We demonstrate the application of iSEE to examine a subset of 379 cells from of mouse visual cortex \citep{tasic2016allen}.
This example can be reproduced locally after installation of the iSEE package with the following code:

@@

\subsection*{Single-cell droplet-based RNA-seq}
% TODO: better title, or do we drop the allen section altogether (above)?
We also demonstrate the use of iSEE to explore a larger data set of 4,000 PBMC single-cell RNA-sequencing dataset from 10X Genomics \citep{zheng2017massively}.
% TODO: take out the juice from what the tour does, and maybe one figure/screenshot in each case?
% embed the allen demo data set
\url{http://shiny.imbei.uni-mainz.de:3838/iSEE_PBMC4k/}
